---
title: "Election Results Viewer"
author: "Roger Toussaint"
date: "December 3, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

suppressPackageStartupMessages(library(tigris))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(sf))
options(tigris_class = 'sf')
```

## Purpose

- The election reults viewer can be used to view who won each election over whom, and which states voted for which party
- This aggregation of several years' data by state is uncommon on the internet

## Mapping

- The tigris package is used for mapping. The following code mimics the mapping performed in the server.R function

```{r, messages = FALSE, warning = FALSE, echo = TRUE, results= 'hide'}
map <- states() %>%
    filter(!(STUSPS %in% c('GU','PR','VI','AK','HI','MP','AS'))) %>%
    st_as_sf() %>%
    ggplot() +
        geom_sf() + 
        theme(
            axis.text.x=element_blank(),axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),axis.text.y=element_blank(),
            axis.title.y=element_blank(),axis.ticks.y=element_blank(),
            legend.title=element_blank(),
            panel.grid.major=element_blank(),
            panel.grid.minor=element_blank(), 
            panel.background=element_blank(),
            panel.border=element_blank()
        )
```

## Map Output

```{r}
map
```

## Links

* The app can be found [here](https://rogerctoussaint.shinyapps.io/Developing_Data_Products_Final_Project/)
* The code can be found [here](https://github.com/Rogerctoussaint/Developing_Data_Products_Final_Project)